---
title: "Lab 01 - Hello R"
author: "Benjamin Egan"
date: "1/16/25"
output: 
  html_document: 
    fig_height: 12
    fig_width: 15
    theme: yeti
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
#type in ?(data) to get the dataset to pull up
```

## Exercises

### Exercise 1

1846 rows
 2 columns (assume x and y)
 variables are: away, bullseye, circle, dino, dots, h_lines, high_lines, slant_down, slant_up, star, v_lines, wide_lines, x_shape

### Exercise 2

Code to create:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Code to calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

Observations:
  | Data pulled from dinosaur dataset
  | ggplot function is being used to graph each datapoint from datasaurus_dozen/dino_data
  | data must be have x and y
  | almost 0 coorelation, makes sense
  


### Exercise 3

Graph of star data

```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
  
  
```

correlation for star data

```{r cor-star}

star_data %>%
  summarize(r = cor(x, y))

```

Observations:
  | star had lots of datapoints around the points but not on the straight parts of the stars


### Exercise 4


Code for circle data

```{r plot-circle, fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Note there's a couple random plot points that are off


```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

Plots for all datasets

```{r plot-all}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~dataset, ncol = 3) +
  theme(legend.position = "none")
```

Correlations for all datasets - not currently doing what it's supposed to do

``` {r cor-all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y))
```

